Data Specialization for a Staged Lambda Calculus

### 2015-01-21 paper/example.tex
migrate overview section's text into semantics section

@@

In this paper, we develop a splitting algorithm
(\ref{sec:splitting,sec:implementation}) which, for any term $e$ in \lang,
produces a pair of terms $e_1,e_2$ containing respectively all the stage \bbone\
and stage \bbtwo\ content of $e$, such that $e_2~e_1$ is equivalent to $e$. In
the case of \texttt{qsStaged}, our splitting algorithm produces the algorithm
described above.

>>>>

\crem{
Notes from 1/16:
\begin{itemize}
\item We are modeling computations where some inputs arrive at stage 1 and
others arrive at stage 2. As a result, some subcomputations can be performed at
stage 1, and others at stage 2.
\item \emph{Statics}: M12 is a language with three worlds: 1, 2, and M.
We model the computations described above as functions in world M.
\item \emph{Dynamics}: We describe how to perform all of the stage 1
subcomputations in an M12 program. Our semantics are mutually defined in terms
of how to reduce terms in each of the three worlds.
\end{itemize}
}

@@

In this paper, we develop a splitting algorithm
(\ref{sec:splitting,sec:implementation}) which, for any term $e$ in \lang,
produces a pair of terms $e_1,e_2$ containing respectively all the stage \bbone\
and stage \bbtwo\ content of $e$, such that $e_2~e_1$ is equivalent to $e$.
(Such a splitting is always possible because $e$ is well-typed in \lang.) In the
case of \texttt{qsStaged}, our splitting algorithm produces the algorithm
described above.
